---
title: "Proyecto Churn"
author: "ADL -Banco Popular"
date: "enero - 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objetivo

Calcular la probabilidad que un cliente con un producto activo en libranza cancele su producto sin haber cumplido el ciclo previamente pactado en la adquisición del producto.

```{r cars}
summary(cars)
```

## Gráfico univariado

You can also embed plots, for example:

```{r pressure, echo=FALSE}
#Ruta
ruta="E:/Jennyfer_C/04_CHURN/BBDD"
setwd(ruta)
load(file="analisis.Rdata")
BBDD<-OBJETIVO_BURO

```


#Histograma
```{r , echo=FALSE}
library("summarytools")
largo_cont<-90
loop.vector_cont <- 2:largo_cont

for (i in loop.vector_cont){ # Loop over loop.vector
  # store data in column.i as x
  x <- BBDD_continua[,i]
  
  # Plot histogram of x
    hist(x,       main = paste(names(BBDD_continua)[i], i), xlab = "")
  boxplot(x,       main = paste(names(BBDD_continua)[i], i), xlab = "")
  boxplot(x~BBDD_continua$TARGET_objetivo,       main = paste(names(BBDD_continua)[i], i), xlab = "", col="orange",
border="brown")
  }
```


#Histograma
```{r , echo=FALSE}
library("summarytools")
largo_cont<-91
loop.vector_cont <- 3:largo_cont

for (i in loop.vector_cont){ # Loop over loop.vector
  # store data in column.i as x
  x <- BBDD_continua[,i]
  
  # Plot histogram of x
  hist(x,       main = paste(names(BBDD_continua)[i], i), xlab = "")
  boxplot(x,       main = paste(names(BBDD_continua)[i], i), xlab = "")
  boxplot(x~BBDD_continua$TARGET_objetivo,       main = paste(names(BBDD_continua)[i], i), xlab = "", col="orange",
border="brown")
  

}
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
